The serious gap laying on healthcare system in Thailand^[Code and data are available at: https://github.com/SANGWOONG-LEE/Thailand_Healthcare]

### 2022-04-05 outputs/paper/paper.Rmd
code cleaning

```{r fig2,echo=FALSE, fig.cap = "Immunization cases between communities"}
#ggplot(data[1:2,], aes(x = Variable, y = Health_Record)) + geom_bar(stat='identity') + facet_wrap(~Mothers_Report)
urban_rural %>%
  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()  +
  labs(x = element_blank(),
       y = "Percent",
       title = "Percentage of Children's Immunization Status by Urban-Rural Area",
       ) +
  theme(legend.title = element_blank())
```

```{r fig3,echo=FALSE, fig.cap = "Immunization cases between region"}
#ggplot(data[3:7,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
region %>%
  ggplot(aes(x = Variable, y = value, fill = immune_status)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()  +
  labs(x = element_blank(),
       y = "Percent",
       title = "Percentage of Children's Immunization Status by Region",
       ) +
  theme(legend.title = element_blank())
```

```{r fig4,echo=FALSE, fig.cap = "Immunization cases between education"}
#ggplot(data[8:11,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
education %>%
  ggplot(aes(x = Variable, y = value, fill = immune_status)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()  +
  labs(x = element_blank(),
       y = "Percent",
       title = "Percentage of Children's Immunization Status by Education",
       ) +
  theme(legend.title = element_blank())
```

```{r fig5,echo=FALSE, fig.cap = "Immunization cases between religion"}
#ggplot(data[12:13,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
religion %>%
  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()  +
  labs(x = element_blank(),
       y = "Percent",
       title = "Percentage of Children's Immunization Status by Religion",
       ) +
  theme(legend.title = element_blank())
```

>>>>

```{r fig2,echo=FALSE, fig.cap = "Immunization cases between communities"}
urban_rural %>%
  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()  +
  labs(x = element_blank(),
       y = "Percent",
       title = "Percentage of Children's Immunization Status by Urban-Rural Area",
       ) +
  theme(legend.title = element_blank())
```

```{r fig3,echo=FALSE, fig.cap = "Immunization cases between region"}
region %>%
  ggplot(aes(x = Variable, y = value, fill = immune_status)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()  +
  labs(x = element_blank(),
       y = "Percent",
       title = "Percentage of Children's Immunization Status by Region",
       ) +
  theme(legend.title = element_blank())
```

```{r fig4,echo=FALSE, fig.cap = "Immunization cases between education"}
education %>%
  ggplot(aes(x = Variable, y = value, fill = immune_status)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()  +
  labs(x = element_blank(),
       y = "Percent",
       title = "Percentage of Children's Immunization Status by Education",
       ) +
  theme(legend.title = element_blank())
```

```{r fig5,echo=FALSE, fig.cap = "Immunization cases between religion"}
religion %>%
  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()  +
  labs(x = element_blank(),
       y = "Percent",
       title = "Percentage of Children's Immunization Status by Religion",
       ) +
  theme(legend.title = element_blank())
```
